On the presentation of orthogonal groups over polynomial rings

### 2019-04-26 dl-paper.tex
Added sheet

\documentclass[oneside, 10pt]{amsart}
\usepackage{amscd, amsmath, amssymb, amsthm, amsfonts, amstext, verbatim, mathtools, xfrac, microtype, nameref, thmtools}
\usepackage[breaklinks=true]{hyperref}
\usepackage[hyperref=true, backend=bibtex, firstinits=true, citestyle=numeric-comp, sortlocale=en_US, url=false, doi=false, eprint=true, maxbibnames=4]{biblatex}
\usepackage[capitalize]{cleveref}
\usepackage[matrix,arrow,curve]{xy}
\usepackage{tikz}
\usepackage{enumitem}
\usepackage[notref,notcite]{showkeys}

@@

\section{Proof of the main result}
\subsection{Overview of the proof}
\subsection{First injectivity theorem}

\begin{prop} Let $\Phi$ be a reduced irreducible root system of type $\neq \rG_2$ and $k$ be arbitrary field.
Then there is a split exact sequence of abelian groups
\[ \xymatrix{ 0 \ar[r] & \K_2(\Phi, k) \ar[r] & \K_2(\Phi, k[X, X^{-1}]) \ar[r] & H(\Phi, k) \ar[r] & 0,}\text{ where} \]
\[ H(\Phi, k) = \left\{\begin{array}{ll} \K_1^\mathrm{MW}(k)& \text{if $\Phi$ is symplectic,}\\ k^* & \text{otherwise.}  \end{array}\right. \]  \end{prop}
\begin{proof} In the nonsymplectic case one can choose a long simple root $\alpha$ of $\Phi$ in such a way that there is a commutative diagram of abelian groups
\[\xymatrixcolsep{5pc}\xymatrix{k^* \ar[r]^-{\{ -, X \}_{\alpha}} \ar[rrd]_{\{-, X\}} & \K_2(\Phi, k[X, X^{-1}]) \ar[r] & \K_2(\Phi, k(X)) \ar[d]^{\cong} \\
                                                                                      &                                 & \K_2^\mathrm{M}(k(X)).} \]
Clearly, the diagonal arrow is injective by Milnor's theorem and the vertical arrow is an isomorphism by Matsumoto's theorem~\cite[Theorem~5.10]{Ma69}.
The required assertion now follow from~\cite[Satz~3]{Hur77} and the fact that the left horizontal arrow is injective.

@@

\subsection{Second injectivity theorem}
\begin{comment}
\[x_{\alpha}(aX^{-1}) x_{-\alpha}(mX) x_{\alpha}(-a(1+am)^{-1}X^{-1}) \cdot \{X, 1+am\} \in G_+.\]
$y := x_{\alpha}(aX^{-1}) x_{-\alpha}(mX) x_{\alpha}(-a(1+am)^{-1}X^{-1})$, 
$z = x_{-\alpha}(-m(1+am)^{-1}X) y h_{\alpha}((1+am)^{-1})$,
Using $\pi(z) = 1$ we get 
\begin{multline}z = z^{h_{ik}^{-1}(X)} = \\ x_{ji}(-m(1+am)^{-1}) x_{ij}(a) x_{ji}(m) \cdot x_{ij}(-a(1+am)^{-1})\{X, (1+am)^{-1}\} \cdot h_{ij}((1+am)^{-1}) \in G. \end{multline}
\end{comment}

@@

 We proceed by case analysis. Let us first analyze the cases when $\beta \neq -\alpha$. In all these cases $m(g) = 0$.
 \begin{enumerate}
 \item {\it Case $\alpha \pm \beta \not \in \Phi \cup \{ 0\}$.}  Obviously, in this case also $g' = g$.
 \begin{comment} 
 \item {\it Case $\alpha + \beta \in \Phi$, $f_1(X) = Xf_1'(X)$, $f_2(X) = 0$.}
 \[ x_\alpha(aX^{-1}) \cdot x_\beta(Xf_1'(X)) = x_{\alpha+\beta}(af_1'(X))x_\beta(Xf_1'(X)) x_\alpha(aX^{-1}) \]
 \end{comment}
 \item {\it Case $\alpha = \beta$.} By our choice of $S$ holds $\beta \not \in \Sigma_S$, therefore $f_2(X) = 0$ and $g$ commutes with $x_\alpha(aX^{-1})$.
 \item {\it Case $\alpha + \beta \in \Phi$, $f_1(X) = Xf_1'(X)$.}
 Direct computation using formula from~\cite[Lemma~9]{S15} shows that:
 \begin{multline*}
 x_\alpha(aX^{-1}) \cdot z_\beta(f_1(X), f_2(X)) = \\ = x_\alpha(af_1'(X)f_2(X)) \cdot x_{\alpha+\beta}(-N_{\beta, \alpha} af_1'(X)) \cdot z_\beta(f_1(X), f_2(X)) \cdot x_\alpha(aX^{-1}); 
 \end{multline*}
 \item {\it Case $\alpha - \beta \in \Phi$, $f_1(X) = Xf_1'(X)$.} Similarly to the above case:
 \begin{multline*}
  x_{\alpha}(aX^{-1}) \cdot z_\beta(f_1(X), f_2(X)) = \\ = x_{\alpha}(-af_1'(X)f_2(X))\cdot x_{\alpha-\beta}(-N_{\beta,-\alpha} af_1'(X)f_2(X)^2) \cdot z_\beta(f_1(X), f_2(X)) \cdot x_{\alpha}(aX^{-1}).
 \end{multline*} \end{enumerate}
Now we turn to the case $\beta = -\alpha$, $f_1(X) = Xf_1'(X)$.
Since $g$ commutes with $x_\alpha(\pm f_2(X))$, it suffices to prove the assertion in the special case $f_2(X)=0$.
First consider the case $f_1(X) = mX$, where $m\in M$. Since $\Phi$ is nonsymplectic, we can choose $\gamma$ such that $\langle \alpha, \gamma \rangle = -1$.
Now direct computation invoking~\eqref{eq:conj-h-h}--\eqref{eq:dennis-stein} and the centrality of symbols shows that:
\begin{multline*}
 x_\alpha(aX^{-1}) \cdot x_{-\alpha}(X m) %= x_\alpha(X^{\langle \alpha, \gamma \rangle}a) x_{-\alpha}(X^{-\langle \alpha, \gamma \rangle}m) 
 = {}^{h_\gamma(X)}(x_\alpha(a) x_{-\alpha}(m)) = \\
 = {}^{h_\gamma(X)}\left( x_{-\alpha}\left(\frac{m}{1+am}\right) \cdot \langle -a, m\rangle_\alpha \cdot h_\alpha(1+am) \cdot x_\alpha\left(\frac{a}{1+am}\right) \right) = \\
 x_{-\alpha}\left(\frac{mX}{1+am}\right) \cdot \langle -a, m\rangle_\alpha \cdot h_\alpha(X^{-1}(1+am))\cdot h_\alpha(X^{-1})^{-1} \cdot x_{\alpha}\left(\frac{aX^{-1}}{1+am}\right) = \\
 x_{-\alpha}\left(\frac{mX}{1+am}\right) \cdot \langle -a, m\rangle_\alpha \cdot \{1+am, X^{-1}\}^{-1} \cdot h_\alpha(1+am)\cdot x_{\alpha}\left(\frac{aX^{-1}}{1+am}\right) = \\
 = x_{-\alpha}\left(\frac{mX}{1+am}\right) \cdot \langle -a, m\rangle_\alpha \cdot h_\alpha(1+am) \cdot x_{\alpha}\left(\frac{aX^{-1}}{1+am}\right) \cdot \{1+am, X\}.
\end{multline*}

@@

\begin{rem}
 From the proof of the above lemma it is easy to describe the way to compute... 
\end{rem}

%\include{rehmann}

>>>>

\documentclass[oneside, 8pt]{amsart}
\usepackage{amscd, amsmath, amssymb, amsthm, amsfonts, amstext, verbatim, mathtools, xfrac, microtype, nameref, thmtools}
\usepackage[breaklinks=true]{hyperref}
\usepackage[hyperref=true, backend=bibtex, firstinits=true, citestyle=numeric-comp, sortlocale=en_US, url=false, doi=false, eprint=true, maxbibnames=4]{biblatex}
\usepackage[capitalize]{cleveref}
\usepackage[matrix,arrow,curve]{xy}
\usepackage{tikz}
\usepackage{enumitem}
\usepackage[notref,notcite]{showkeys}

@@

\section{First injectivity theorem}
\begin{prop} Let $\Phi$ be a reduced irreducible root system of type $\neq \rG_2$ and $k$ be arbitrary field.
Then there is a split exact sequence of abelian groups
\[ \xymatrix{ 0 \ar[r] & \K_2(\Phi, k) \ar[r] & \K_2(\Phi, k[X, X^{-1}]) \ar[r] & H(\Phi, k) \ar[r] & 0,}\text{ where} \]
\[ H(\Phi, k) = \left\{\begin{array}{ll} \K_1^\mathrm{MW}(k)& \text{if $\Phi$ is symplectic,}\\ k^* & \text{otherwise.}  \end{array}\right. \]  \end{prop}
\begin{proof} In the nonsymplectic case one can choose a long simple root $\alpha$ of $\Phi$ in such a way that there is a commutative diagram of abelian groups
\[\xymatrixcolsep{5pc}\xymatrix{k^* \ar[r]^-{\{ -, X \}_{\alpha}} \ar[rrd]_{\{-, X\}} & \K_2(\Phi, k[X, X^{-1}]) \ar[r] & \K_2(\Phi, k(X)) \ar[d]^{\cong} \\
                                                                                      &                                 & \K_2^\mathrm{M}(k(X)).} \]
Clearly, the diagonal arrow is injective by Milnor's theorem and the vertical arrow is an isomorphism by Matsumoto's theorem~\cite[Theorem~5.10]{Ma69}.
The required assertion now follow from~\cite[Satz~3]{Hur77} and the fact that the left horizontal arrow is injective.

@@

\begin{comment}
\[x_{\alpha}(aX^{-1}) x_{-\alpha}(mX) x_{\alpha}(-a(1+am)^{-1}X^{-1}) \cdot \{X, 1+am\} \in G_+.\]
$y := x_{\alpha}(aX^{-1}) x_{-\alpha}(mX) x_{\alpha}(-a(1+am)^{-1}X^{-1})$, 
$z = x_{-\alpha}(-m(1+am)^{-1}X) y h_{\alpha}((1+am)^{-1})$,
Using $\pi(z) = 1$ we get 
\begin{multline}z = z^{h_{ik}^{-1}(X)} = \\ x_{ji}(-m(1+am)^{-1}) x_{ij}(a) x_{ji}(m) \cdot x_{ij}(-a(1+am)^{-1})\{X, (1+am)^{-1}\} \cdot h_{ij}((1+am)^{-1}) \in G. \end{multline}

@@

 We proceed by case analysis. Let us first analyze the cases when $\beta \neq -\alpha$. In all these cases $m(g) = 0$.
 \begin{enumerate}
 \item {\it Case $\alpha \pm \beta \not \in \Phi \cup \{ 0\}$.}  Obviously, in this case also $g' = g$.
 \item {\it Case $\alpha + \beta \in \Phi$, $f_1(X) = Xf_1'(X)$, $f_2(X) = 0$.}
 \[ x_\alpha(aX^{-1}) \cdot x_\beta(Xf_1'(X)) = x_{\alpha+\beta}(af_1'(X))x_\beta(Xf_1'(X)) x_\alpha(aX^{-1}) \]
 \item {\it Case $\alpha = \beta$.} By our choice of $S$ holds $\beta \not \in \Sigma_S$, therefore $f_2(X) = 0$ and $g$ commutes with $x_\alpha(aX^{-1})$.
 \item {\it Case $\alpha + \beta \in \Phi$, $f_1(X) = Xf_1'(X)$.}
 Direct computation using formula from~\cite[Lemma~9]{S15} shows that:
 \begin{multline*}
 x_\alpha(aX^{-1}) \cdot z_\beta(f_1(X), f_2(X)) = \\ = x_\alpha(af_1'(X)f_2(X)) \cdot x_{\alpha+\beta}(-N_{\beta, \alpha} af_1'(X)) \cdot z_\beta(f_1(X), f_2(X)) \cdot x_\alpha(aX^{-1}); 
 \end{multline*}
 \item {\it Case $\alpha - \beta \in \Phi$, $f_1(X) = Xf_1'(X)$.} Similarly to the above case:
 \begin{multline*}
  x_{\alpha}(aX^{-1}) \cdot z_\beta(f_1(X), f_2(X)) = \\ = x_{\alpha}(-af_1'(X)f_2(X))\cdot x_{\alpha-\beta}(-N_{\beta,-\alpha} af_1'(X)f_2(X)^2) \cdot z_\beta(f_1(X), f_2(X)) \cdot x_{\alpha}(aX^{-1}).
 \end{multline*} \end{enumerate}
Now we turn to the case $\beta = -\alpha$, $f_1(X) = Xf_1'(X)$.
Since $g$ commutes with $x_\alpha(\pm f_2(X))$, it suffices to prove the assertion in the special case $f_2(X)=0$.
First consider the case $f_1(X) = mX$, where $m\in M$. Since $\Phi$ is nonsymplectic, we can choose $\gamma$ such that $\langle \alpha, \gamma \rangle = -1$.
Now direct computation invoking~\eqref{eq:conj-h-h}--\eqref{eq:dennis-stein} and the centrality of symbols shows that:
\begin{multline*}
 x_\alpha(aX^{-1}) \cdot x_{-\alpha}(X m) %= x_\alpha(X^{\langle \alpha, \gamma \rangle}a) x_{-\alpha}(X^{-\langle \alpha, \gamma \rangle}m) 
 = {}^{h_\gamma(X)}(x_\alpha(a) x_{-\alpha}(m)) = \\
 = {}^{h_\gamma(X)}\left( x_{-\alpha}\left(\frac{m}{1+am}\right) \cdot \langle -a, m\rangle_\alpha \cdot h_\alpha(1+am) \cdot x_\alpha\left(\frac{a}{1+am}\right) \right) = \\
 x_{-\alpha}\left(\frac{mX}{1+am}\right) \cdot \langle -a, m\rangle_\alpha \cdot h_\alpha(X^{-1}(1+am))\cdot h_\alpha(X^{-1})^{-1} \cdot x_{\alpha}\left(\frac{aX^{-1}}{1+am}\right) = \\
 x_{-\alpha}\left(\frac{mX}{1+am}\right) \cdot \langle -a, m\rangle_\alpha \cdot \{1+am, X^{-1}\}^{-1} \cdot h_\alpha(1+am)\cdot x_{\alpha}\left(\frac{aX^{-1}}{1+am}\right) = \\
 = x_{-\alpha}\left(\frac{mX}{1+am}\right) \cdot \langle -a, m\rangle_\alpha \cdot h_\alpha(1+am) \cdot x_{\alpha}\left(\frac{aX^{-1}}{1+am}\right) \cdot \{1+am, X\}.
\end{multline*}

@@

\begin{rem}
 From the proof of the above lemma it is easy to describe the way to compute... 
\end{rem}
\include{rehmann}
\end{comment}

\section{Second injectivity theorem}
\begin{comment} 
First of all, set $\widetilde{V} = \overline{G}^{\geq 0}_M \times G^{\leq 0} \times (1 + M)^*$
 and consider it as a pointed set, i.\,e. ignore its structure of the group but retain $\widetilde{v_0} = (1, 1, 1)$ as a choice of a basepoint.
We let the group $\St(\Phi, R, M)$ act on $\widetilde{V}$ via the formula 
 $h \cdot (\overline{g}^+, g^-, u) = (\overline{g}^+ \cdot j_+i_+(h), i_-(h)^{-1}\cdot g^-, u)$.
Denote by $V$ the set of orbits of this action with the fixed basepoint $v_0 = O(\widetilde{v}_0)$.
We will use the notation $[\overline{g}^+, g^-, u]$ as a shorthand for $O(\overline{g}^+, g^-, u)$.

It is obvious that the map $\widetilde{p} \colon \widetilde{V} \to \St(\Phi, R[t, t^{-1}])$ given by 
 \[(\overline{g}^+, g^-, u) \mapsto \overline{g}^+ \cdot j_-(g^-) \cdot \{t, u\}\]
 is constant on the orbits of the above action
  and therefore gives rise to a well-defined map $p \colon V \to \St(\Phi, R[t, t^{-1}])$ of pointed sets.

We will construct an action of $\St(\Phi, B)$ on the set $V$ with the following additional properties:
\begin{enumerate}
\item for $g^- \in \St(\Phi, R[t^{-1}])$ one has $\varphi(g^-) \cdot v_0 = [1, g^-, 1]$, where $\varphi$ is the canonical map
  $\St(\Phi, R[t^{-1}]) \to \St(\Phi, B)$ induced by the embedding $R[t^{-1}] \to B$.
\item for $g \in \St(\Phi, B)$ the element $p(g \cdot v_0)$ coincides with the canonical image of $g$ in $\St(\Phi, R[t, t^{-1}])$; 
\end{enumerate} \end{comment}

Throughout this section $\Phi$ is a simply-laced irreducible root system and $R$ is a local ring with maximal ideal $M$.
We denote by $B$ the ring $M[t] + R[t^{-1}]$ considered as a graded subring of $R[t, t^{-1}]$.
Denote by $\overline{G}^{\geq 0}_M$ the image of the map $\St(\Phi, R[t], M[t]) \to \St(\Phi, R[t, t^{-1}])$ and by
 $G^{\leq 0}$ the group $\St(\Phi, R[t^{-1}])$.

\[ \xymatrix{ \overline{\St}(\Phi, R, M) \ar[r]^{j_+i_+} \ar[d]^{i^-} & \overline{G}_M^{\geq 0} \ar@{^{(}->}[d] \\
              G^{\leq 0} \ar[r]^{j_-} & \St(\Phi, R[t, t^{-1}]), } \]

\subsection{Some elementary lemmas}
\begin{comment}
Hall-Witt identity
\[ [[ y^{-1}, x], z] ^ {y^{-1}}  [[ z^{-1}, y], x] ^ {z^{-1}}  [[ x^{-1}, z], y] ^ {x^{-1}} = 1 \]
\[ [[ y^{-1}, x], z]  \cdot [[ z^{-1}, y], x] ^ {z^{-1}y} \cdot  [[ x^{-1}, z], y] ^ {x^{-1}y} = 1. \]
\[ [[ z^{-1}, y^{-1}], x] ^ {z^{-1}y^{-1}} \cdot  [[ x^{-1}, z], y^{-1}] ^ {x^{-1}y^{-1}} = [z, [ y, x]] . \]
\[  . \]
\end{comment}

The following lemma summarizes basic properties of structure constants used in our computations below.
\begin{lemma} Suppose $\Phi$ is simply laced and $\alpha, \beta \in \Phi$ are such that $\alpha+\beta = \gamma \in \Phi$.
\begin{enumerate}
 \item $N_{\alpha, \beta} = -N_{\beta,\alpha}$;
 \item $N_{\alpha, \beta} = - N_{-\alpha, -\beta}$;
 \item $N_{\alpha, \beta} = N_{\beta, \gamma} = N_{\gamma, \alpha}.$
\end{enumerate}
\end{lemma}
\begin{proof} See~\cite[\S~14]{VP}. \end{proof}

Recall that $z_\alpha(s, \xi) := x_\alpha(s)^{x_{-\alpha}(\xi)}$.
\begin{lemma}\label{Zrels} Let $\Phi$ be a simply laced root system and $\alpha,\beta\in \Phi$ be a pair of roots. The elements $z_\alpha(s, \xi)$ satisfy the following relations (everywhere below $\xi, \eta\in R$, $s\in I$):
\begin{enumerate} 
\item\label{Z1} $z_{\alpha}(s, \xi) ^ {x_{-\alpha}(\eta)} = z_{\alpha}(s, \xi + \eta)$;
\item\label{Z2} $z_{\beta}(s, \xi) ^ {x_{-\alpha}(\eta)} = x_{-\alpha} (- s\xi \eta) \cdot x_{\beta-\alpha} (N_{\beta, -\alpha}\cdot s\eta)     \cdot z_{\beta}(s, \xi)\ \text{if}\ \alpha - \beta \in \Phi$;
\item\label{Z3} $z_{\beta}(s, \xi) ^ {x_{-\alpha}(\eta)} = x_{-\alpha} (s\xi \eta) \cdot x_{-\alpha-\beta} (N_{\beta,\alpha}\cdot s\xi^2\eta) \cdot z_{\beta}(s, \xi)\ \text{if}\ \alpha + \beta \in \Phi$;
\item\label{Z4} $z_{\gamma}(s, \xi) ^ {x_{-\alpha}(\eta)} = z_{\gamma}(s, \xi)\ \text{if}\ \gamma\perp\alpha$.
\item\label{Z5} $z_{\alpha+\beta}(st, \xi) = x_{-\beta}(-s\xi) \cdot x_\alpha(N_{\alpha,\beta}s) \cdot x_{-\alpha}(N_{\alpha,\beta}st^2\xi^2) \cdot x_{-\alpha-\beta}(-st\xi^2) \cdot z_{-\beta}(-s\xi, -t) \cdot x_{\beta}(-st^2\xi)  \cdot x_{\alpha+\beta}(-st) \cdot z_\alpha(N_{\alpha,\beta} s, -N_{\alpha, \beta}t\xi).$
\end{enumerate} \end{lemma}
\begin{proof}
The first four assertions are contained in~\cite[Lemma~9]{S15}. For the proof of the last formula set $\gamma = \alpha + \beta$ and compute:
\begin{multline} z_{\gamma}(N_{\alpha,\beta}st, \xi) = 
[x_\alpha(s)^{x_{-\gamma}(\xi)}, x_\beta(t)^{x_{-\gamma}(\xi)}] = [x_{-\beta}(N_{\alpha, -\gamma} s\xi) \cdot x_\alpha(s),\ x_{-\alpha}(N_{\beta, -\gamma}t\xi) \cdot x_\beta(t)] = \\ = x_{-\beta}(N_{\alpha, -\gamma} s\xi) \cdot x_\alpha(s) \cdot \left( x_{-\beta}(N_{\alpha, -\gamma} s\xi) \cdot x_\alpha(s)\right)^{x_{-\alpha}(-N_{\beta, -\gamma}t\xi) \cdot x_\beta(-t)} = \\
= x_{-\beta}(N_{\alpha, -\gamma} s\xi) \cdot x_\alpha(s) \cdot z_{-\beta}(N_{\alpha, -\gamma} s\xi, -t)^{x_{-\alpha}(-N_{\beta, -\gamma}t\xi)} \cdot z_\alpha(s, -N_{\beta, -\gamma}t\xi)^ {x_\beta(-t)} = \\
= x_{-\beta}(N_{\alpha, -\gamma} s\xi) \cdot x_\alpha(s) \cdot x_{-\alpha}(-N_{\alpha, -\gamma}N_{\beta, -\gamma}st^2\xi^2) \cdot x_{-\gamma}(-N_{-\beta, -\alpha} N_{\alpha, -\gamma} N_{\beta, -\gamma}st\xi^2) \cdot z_{-\beta}(N_{\alpha, -\gamma} s\xi, -t) \cdot \\ \cdot x_{\beta}(-N_{\beta,-\gamma}st^2\xi)  \cdot x_{\gamma}(-N_{\alpha, \beta}st) \cdot z_\alpha(s, -N_{\beta, -\gamma}t\xi) =\\ = x_{-\beta}(-N_{\alpha, \beta} s\xi) \cdot x_\alpha(s) \cdot x_{-\alpha}(st^2\xi^2) \cdot x_{-\gamma}(-N_{\alpha, \beta} st\xi^2) \cdot z_{-\beta}(-N_{\alpha, \beta} s\xi, -t) \cdot x_{\beta}(-N_{\alpha, \beta}st^2\xi)  \cdot x_{\gamma}(-N_{\alpha, \beta}st) \cdot z_\alpha(s, -N_{\alpha, \beta}t\xi). \qedhere
\end{multline}  
In the last equality we invoked the standard properties of structure constants (see e.\,g. formulas in Vavilov-Plotkin \S~14 which imply in our case that $N_{\alpha, \beta} = N_{\beta,-\gamma} = N_{-\gamma, \alpha} = -N_{\alpha, -\gamma}$).
\end{proof}

Using a variant of Hall-Witt identity: $[x, [ y, z]] = [[ x^{-1}, y^{-1}], z] ^ {x^{-1}y^{-1}} \cdot  [[ z^{-1}, x], y^{-1}] ^ {z^{-1}y^{-1}}$ we compute
\begin{multline}
 [x_\alpha(m), x_{-\alpha}(X\xi)] = [x_\alpha(m), [x_{-\alpha-\beta}(N_{-\alpha-\beta, \beta} X), x_{\beta}(\xi)]] = \\ = \left([[ x_\alpha(m), x_{-\alpha-\beta}(-N_{-\alpha-\beta, \beta}X)], x_{\beta}(\xi)] ^ {x_\alpha(-m)} \cdot  [[ x_{\beta}(-\xi), x_\alpha(m)], x_{-\alpha-\beta}(-N_{-\alpha-\beta, \beta}X)] ^ {x_{\beta}(-\xi)}\right)^{x_{-\alpha-\beta}(-N_{-\alpha-\beta, \beta}X)} = \\ = \left([x_{-\beta}(-N_{-\alpha-\beta,\beta}N_{\alpha,-\alpha-\beta}mX), x_{\beta}(\xi)] ^ {x_\alpha(-m)} \cdot  [ x_{\alpha + \beta}(-N_{\beta, \alpha}m\xi), x_{-\alpha-\beta}(-N_{-\alpha-\beta, \beta}X)] ^ {x_{\beta}(-\xi)}\right)^{x_{-\alpha-\beta}(-N_{-\alpha-\beta, \beta}X)} =
\end{multline}

\subsection{Computation of the kernel of the map of evaluation at $0$.}
\begin{lemma} Denote by $C$ the mutual commutator subgroup $\left[\St(\Phi, XA[X]), \overline{\St}(\Phi, A, M)\right]$.
Then one has \[\overline{\St}(\Phi, A[X], M[X]) = \overline{\St}(\Phi, A, M) \cdot \overline{\St}(\Phi, A[X], XM[X]) \cdot C.\] 
Consequently, the composite of the two factors in the right-hand side of the above formula coincides with the subgroup $I$ defined as 
 the intersection $\overline{\St}(\Phi, A[X], M[X]) \cap \overline{\St}(\Phi, A[X], XA[X])$ (or alternatively, as the kernel of the evaluation map $\overline{\St}(\Phi, A[X], M[X]) \to \overline{\St}(\Phi, A, M)$).
\end{lemma}
\begin{proof}
 Take $g \in \overline{\St}(\Phi, A[X], M[X])$ and write it as $g = \prod_i z_{\alpha_i}(f_i(X), \xi_i(X))$ for some $f_i(X) = f_i(0) + Xf_i'(X) \in M[X]$, $\xi_i(X) = \xi_i(0) + X\xi_i'(X) \in A[X]$.
 It is clear that modulo $\overline{\St}(\Phi, A[X], XM[X])$ the element $g$ is congruent to $g_1(X) = \prod_i z_{\alpha_i}(f_i(0), \xi_i(X)).$

 Now each factor $z_{\alpha_i}(f_i(0), \xi_i(X))$ can written as $z_{\alpha_i}(f_i(0), \xi_i(0))^{x_{-\alpha_i}(X\xi'_i(X))} = [x_{-\alpha_i}(X\xi'_i(X)), z_{\alpha_i}(f_i(0), \xi_i(0))] \cdot z_{\alpha_i}(f_i(0), \xi_i(0))$.
 Using the fact that the subgroup $\left[\St(\Phi, XA[X]), \overline{\St}(\Phi, A, M)\right]$ is normalized by $\St(\Phi, A, M)$ (this follows e.\,g. from the formula $[g, h]^{h_1} = [h_1^{-1}, g][g, h_1^{-1}h]$) we conclude that $g_1(X)$ is congruent to $g(0) = g_1(0)$ modulo $C$, which implies the first assertion.

 Denote by $H$ the composite of $C$ and $\overline{\St}(\Phi, A[X], XM[X])$. It is clear that $H \subseteq I$. The reverse inclusion follows from the above argument and the fact that for $g \in I$ one has $g(0)=1$. \qedhere \end{proof}

 \begin{lemma}
   If $R$ is a local ring with maximal ideal $M$ then $\overline{\St}(\Phi, R, M) = U(\Phi^+, M) \cdot M(\Phi, R, M) \cdot U(\Phi^-, M)$.
 \end{lemma}
 \begin{proof}
  See Theorem~2.4 of~M. Stein's paper on surjective stability in dimension 0.
 \end{proof}

\begin{corollary} For $R$, $M$ as above holds
 $\left[\St(\Phi, XR[X]), \overline{\St}(\Phi, R, M)\right] \subseteq \St(\Phi, XM[X]) \cdot \left[\St(\Phi, XR[X]), \St(\Phi, M)\right]$.
\end{corollary}
\begin{proof}
 Notice first that the generators of $M(\Phi, R, M)$ normalize both $\St(\Phi, XA[X])$ and $\St(\Phi, M)$ (see eq:conj-h-x).
 Now for $g \in \St(\Phi, XR[X])$, $h \in M(\Phi, R, M)$, $u^+ \in U(\Phi^+, M)$, $u^- \in U(\Phi^-, M)$ holds:
 \[ [g, h u^+ u^-] = [g, h] \cdot [{}^{h}\!g, {}^{h}\!(u^+u^-)] \in \St(\Phi, XM[X]) \cdot [\St(\Phi, XR[X]), \St(\Phi, M)]. \qedhere\]
\end{proof}

\begin{corollary} For $R$ and $M$ as above the subgroup $I$ is generated as a group by its subgroup $\St(\Phi, R[X], XM[X])$ and
 the elements $[x_\alpha(m), x_{-\alpha}(X\xi)]$, $m \in M$, $\xi \in R[X]$, $\alpha \in \Phi$. 
\end{corollary}
\begin{proof}
By the above lemmata one has $I \subseteq \St(\Phi, R[X], XM[X]) \cdot [\St(\Phi, XR[X]), \St(\Phi, M)].$
It is clear that modulo $\St(\Phi, R[X], XM[X])$ the commutator subgroup $[\St(\Phi, XR[X]), \St(\Phi, M)]$ is generated
 by all $[x_\alpha(m), x_{-\alpha}(X\xi)]^g$, $m \in M$, $\xi \in R[X]$, where $g \in \St(\Phi, M + XR[X])$.
To verify the assertion, therefore, it remains to show that the commutators $[[x_\alpha(m), x_{-\alpha}(X\xi)], g]$ belong to $\St(\Phi, R[X], XM[X])$.
Moreover, since the latter subgroup is normal it suffices to prove this inclusion in the special case when $g$ is a generator of $\St(\Phi, R[X])$,
i.\,e. $g = x_\beta(\xi)$, $\eta \in R[X]$. Without loss of generality we may assume $\alpha \neq \pm \beta$.

Set $c_{\alpha,\beta}(m,\xi,\eta) = [[x_{\alpha}(m), x_{-\alpha}(X\xi)], x_\beta(\eta)]$.
If $\alpha + \beta \not\in \Phi$, $\alpha - \beta \not \in \Phi$ then, obviously, one has $c_{\alpha,\beta}(m,\xi,\eta) = 1$.
Now suppose $\alpha + \beta \in \Phi$, $\alpha - \beta \in \Phi$. We have:
\begin{multline} \nonumber c_{\alpha,\beta}(m,\xi,\eta) = [x_{\alpha}(m), x_{-\alpha}(X\xi)] [x_{-\alpha}(X\xi), x_{\alpha}(m)x_{\alpha+\beta}(N_{\beta,\alpha} m\eta)] = \\
 = {}^{x_\alpha(m)}\![x_{-\alpha}(X\xi), x_{\alpha + \beta}(N_{\beta, \alpha}m\eta)] = x_{\beta}(N_{\beta,\alpha} N_{-\alpha, \alpha+\beta} mX\xi\eta) x_{\alpha+\beta}(N_{\alpha,\beta}N_{\beta,\alpha}N_{-\alpha, \alpha+\beta}m^2X\xi\eta). 
\end{multline}
It is clear that the expression in the right-hand side belongs to $\St(\Phi, R[X], XM[X])$. In the case $\alpha - \beta \in \Phi$, $\alpha + \beta \not \in \Phi$ the computation is similar.
{\bf TODO:} we have to consider more cases if we want to make the result valid for nonsimply-laced root systems.
\end{proof}

\subsection{The subgroups $P_\alpha(0)$, $P_\alpha(*)$ and their properties.} Throughout this subsection $\alpha$ denotes some fixed root of $\Phi$.
\begin{df} \label{defP0}
Denote by $P_\alpha(0)$ the subgroup of $\St(\Phi, R[X, X^{-1}])$ generated by the images of the following elements of $\St(\Phi, R[X])$ under the
 map induced by the embedding $R[X] \subseteq R[X, X^{-1}]$:
\begin{enumerate}
 \item $z_{\beta}(Xf, g), \beta \in \Phi \text{ such that }\alpha + \beta \in \Phi\text{ or } \alpha - \beta \in \Phi;$
 \item $z_{\beta}(f, Xg),\ \beta \in \Phi \text{ such that }\alpha - \beta \in \Phi \cup \{0\};$
 \item $z_{\gamma}(f, g),\ \alpha \perp \gamma;$
 \item $x_{-\alpha}(X^2f),$
 \item $[x_{\beta}(m), x_{-\beta}(Xg)],\ \beta \in \Phi \text{ such that }\alpha + \beta \in \Phi$.
\end{enumerate}
In the above formulae and below we assume that $f \in M[X]$ and $g \in R[X]$. \end{df}

Denote by $P_\alpha(*)$ the subgroup of $\St(\Phi, R[X, X^{-1}])$ generated by $P_\alpha(0)$ and the elements $x_{-\alpha}(mX)$, $m \in M$. The following lemma shows that this subgroup is sufficiently large.
\begin{lemma} The subgroup $P_\alpha(*)$ contains the image of the subgroup $\St(\Phi, R[X], XM[X])$ in $\St(\Phi, R[X, X^{-1}])$. \end{lemma}
\begin{proof}
Clearly $P_\alpha(*)$ contains the elements $x_\beta(Xf)$ for all $\beta \in \Phi$ and $z_\beta(Xf, g)$ for $\beta \in \Phi \setminus \{\pm \alpha\}$, $f \in M[X]$, $g\in R[X]$.
The assertion now easily follows from Stepanov's theorem. This can also be verified in a straightforward manner without Stepanov theorem.

Now let us verify the assertion for the generators $c_\beta(m, \xi) = [x_\beta(m), x_{-\beta}(X\xi)] = x_\beta(m) \cdot z_{\beta}(-m, -X\xi)$.
It is clear that $c_\beta(m, \xi)$ are contained in $P_\alpha(*)$ in the cases $\beta \perp \alpha$, $\alpha - \beta \in \Phi \cup \{0\}$.
There are problems: 1) for the generator $c_{-\alpha}(m, \xi)$, 2) for the generator $c_\beta(m, \xi)$, $\alpha + \beta \in \Phi$.

\begin{comment}
Let us draw the matrix for $z_\alpha(m, X\xi)$:
\[ \left(\begin{array}{cc} 1 & 0 \\ -X\xi & 1 \end{array} \right) \cdot \left(\begin{array}{cc} 1 & m \\ 0 & 1 \end{array} \right) \cdot \left(\begin{array}{cc} 1 & 0 \\ X\xi & 1 \end{array} \right) = 
 \left(\begin{array}{cc} 1 & m \\ -X\xi & 1 - mX\xi \end{array} \right) \cdot \left(\begin{array}{cc} 1 & 0 \\ X\xi & 1 \end{array} \right) = \left(\begin{array}{cc} 1 + mX\xi & m \\ -mX^2\xi^2 & 1 - mX\xi \end{array} \right) \]
Now let us draw the matrix for $c_\alpha(m, \xi)$:
\[ \left(\begin{array}{cc} 1 & m \\ 0 & 1 \end{array} \right) \left(\begin{array}{cc} 1 + mX\xi & -m \\ mX^2\xi^2 & 1 - mX\xi \end{array} \right) = 
 \left(\begin{array}{cc} 1 + mX\xi + m^2X^2\xi^2 & -m^2X\xi \\ mX^2\xi^2 & 1 - mX\xi \end{array} \right) \] 
\end{comment}
\end{proof}
